Appendix S1: Supporting Tables and Figures.

### 2022-06-26 ms/SI.Rmd
fix fig centering

---
title: "Appendix S1: Supporting Tables and Figures."
#title: "Maenpuen *et al.* --American Journal of Botany-- Appendix S1"
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
#font-famliy: "ebgaramond"
mainfont: Arial
sansfont: Arial
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{caption}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1} # add header on right side
 # - \captionsetup[figure]{name=Figure S} #  - \usepackage{lineno}
#  - \linenumbers
output:
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: FALSE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
      toc: true
  bookdown::pdf_document2:
    citation_package: default
    toc: yes
    number_sections: no
    fig_caption: no
    keep_tex: yes
    # template: templates/eisvogel2.tex
---

@@

```{r, echo=FALSE, caption = "hopge"}
library(jsonlite)
site <- fromJSON(here("data", "site_info.json"))
site2 <- t(site)
site2[1,] <- t(site)[2,]
site2[2,] <- t(site)[1,]
colnames(site2) <- site2[1,]
site2 <- site2[-1,]
site2 |>
  kbl(booktabs = TRUE, escape = FALSE, format = "latex") |>
  #kable(format = "simple") |>
    # caption = "Site information.
    #           MAT: mean annual temperature,
    #           MAP: mean annual precipitation,
    #           CV: coefficient of variation") |>
  kable_styling(latex_options = c("striped", "HOLD_position")) |>
  column_spec(1:5, width = "3cm")# |>
#  kableExtra::landscape()
```

@@

![](../figs/S2.jpeg){ width="470" style="display: block; margin: 0 auto" }

@@

![](../figs/lma_ld.pdf){ width="600" style="display: block; margin: 0 auto" }

>>>>

---
title: "Appendix S1: Supporting Tables and Figures."
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
header-includes:
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{colortbl}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \usepackage[default]{sourcesanspro}
  - \usepackage{sourcecodepro}
  - \fancypagestyle{plain}{\pagestyle{fancy}}
  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1}
output:
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: FALSE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
      toc: true
  bookdown::pdf_document2:
    citation_package: default
    toc: yes
    number_sections: no
    fig_caption: no
    keep_tex: yes
    # template: templates/eisvogel2.tex
---

@@

```{r, echo=FALSE, caption = "hopge"}
library(jsonlite)
site <- fromJSON(here("data", "site_info.json"))
site2 <- t(site)
site2[1,] <- t(site)[2,]
site2[2,] <- t(site)[1,]
colnames(site2) <- site2[1,]
site2 <- site2[-1,]
site2 |>
  kbl(booktabs = TRUE, escape = FALSE, format = "latex") |>
  kable_styling(latex_options = c("striped", "HOLD_position")) |>
  column_spec(1:5, width = "3cm")
```

@@

::: {.center data-latex=""}
![](../figs/S2.jpeg){ width=470 margin=auto }
:::

@@

![](../figs/lma_ld.pdf){ width="600" style="display: block; margin: 0 auto; align: center" }
